---
title: "Main analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```

```{r libraries}
library(tidyverse)  
library(here)
library(patchwork)
library(broom.mixed)
library(ggrepel)
library(glmmTMB)
library(ggtext)
library(xtable)
library(scales)
library(brms)
library(ordbetareg)
library(loo)
library(purrr) 
library(marginaleffects)
library(collapse)

select <- dplyr::select
```

This notebook contains our main analysis that examines the relationship between lexicalization and its predictor variables as well as part-of-speech analysis.

# Visualize the relation between lexicalization and usage frequency

```{r main fig 1, include=TRUE}
set.seed(123)

d_full <- read_csv(here("data", "d_full.csv"), show_col_types = FALSE) %>%
  mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.)))

dplot <- d_full %>%
  pivot_longer(cols = c("lex_wold", "lex_ids"), names_to = "row_group", values_to = "lex_freq") %>%
  pivot_longer(cols = c("wl_mean", "do_mean", "en"), names_to = "column_group", values_to = "log_mean") %>%
  mutate(row_group = case_when(
    row_group == "lex_wold" ~ "WOLD",
    row_group == "lex_ids" ~ "IDS"
  )) %>%
  mutate(column_group = case_when(
    column_group == "wl_mean" ~ "Worldlex",
    column_group == "do_mean" ~ "DoReCo",
    column_group == "en" ~ "English only"
  )) %>%
  mutate(
    row_group = factor(row_group, levels = c("IDS", "WOLD")),
    column_group = factor(column_group, levels = c("DoReCo", "Worldlex", "English only"))
  ) %>%
  mutate(lex_freq = ifelse(lex_freq >= 1, 1, lex_freq))

fit_beta_model <- function(data) {
  model <- glmmTMB(lex_freq ~ log_mean, data = data, family = ordbeta(link = "logit"))
  data$predicted <- predict(model, type = "response")
  return(data)
}

dplot_with_pred <- dplot %>%
  group_by(row_group, column_group) %>%
  do(fit_beta_model(.))

plot <- dplot_with_pred %>%
  ggplot(aes(x = log_mean, y = lex_freq)) +
  geom_point(alpha = 0.3, size = 0.01, color = "black") +
  geom_line(aes(x = log_mean, y = predicted), color = "blue", linewidth = 0.5) +
  facet_grid(row_group ~ column_group, scales = "free_x") +
  labs(
    x = "Log mean usage frequency per million",
    y = "Lexicalization score"
  ) +
  scale_x_continuous(breaks = scales::pretty_breaks(n = 5)) +
  theme_minimal(base_size = 9) +
  theme(
    plot.title = element_blank(),
    plot.subtitle = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(face = "bold", size = 7.875),
    panel.grid = element_blank(),
    panel.background = element_rect(fill = "white", color = NA),
    panel.spacing = unit(0.1, "lines"),
    axis.line.x = element_blank(),
    axis.line.y = element_blank(),
    axis.text.x = element_text(size = 6.75),
    axis.text.y = element_text(size = 6.75),
    panel.border = element_rect(color = "gray70", fill = NA, linewidth = 0.3),
    plot.margin = margin(1, 1, 1, 1)
  )

swadesh  <- c("I","you","we","this","that","who","what","not","all","many","one",
              "two","big","long","small","woman","man","person","fish","bird",
         "dog","louse","tree","seed","leaf","root","bark","skin","flesh","blood",
         "bone","grease","egg","horn","tail","feather","hair","head","ear","eye",
         "nose","mouth","tooth","tongue","claw","foot","knee","hand","belly","neck",
         "breast","heart","liver","drink","eat","bite","see","hear","know","sleep",
         "die","kill","swim","fly","walk","come","lie","sit","stand","give","say",
         "sun","moon","star","water","rain","stone","sand","earth","cloud",
         "smoke","fire","ash","burn","path","mountain","red","green","yellow",
         "white","black","night","hot","cold","full","new","good","round","dry","name")

leipzig <- c("fire","nose","go","water","mouth","tongue","blood","bone","root","come",
             "breast","rain","name","louse","wing","flesh","meat","arm","hand","fly",
         "night","ear","neck","far","do","house","stone","bitter","say","tooth","hair",
         "big","one","who","hit","beat","leg","foot",
         "horn","this","fish","yesterday","drink","black","navel","stand","bite","back",
         "wind","smoke","what","child","egg","give","new","burn","not","good",
         "know","knee","sand","laugh","hear","soil","leaf","red","liver","hide","skin",
         "suck","carry","ant","heavy","take","old","eat","thigh","thick",
         "long","blow","wood","run","fall","eye","ash","tail","dog","cry","weep","tie",
         "see","sweet","rope","shade","shadow","bird","salt","small",
         "wide","star","in","hard","crush","grind") 
# these are not included: 2sg pronoun, 1sg pronoun

nsm <- c("I","you","person","thing","body","this","same","other","one","two","some","all",
         "many","good","bad","big","small","think","know","want",
         "feel","see","hear","say","word","true","do or make","happen","move","touch",
         "have","be alive","be dead","when","now","before","after","moment",
         "where","place","time","here","above","below","far","near","side",
         "inside","not","maybe","can","because","if","very","more","be", 
         "someone","something", "me", "people", "part", "much", "little", "few")
# these are not included: there is, a long time, a short time, for some time, kind of, don't want, be someone's, be someone/something, like-way-as

lists <- c(swadesh, leipzig, nsm) %>% unique()

total <- length(unique(d_full$concepticon_id))

both <- d_full %>%
  mutate(ranklex_w = rank(lex_wold) / total,
         ranklex_i = rank(lex_ids) / total,
         rankmean_w = rank(wl_mean) / total,
         rankmean_r = rank(do_mean) / total) %>%
  mutate(concepticon_gloss = str_replace(concepticon_gloss, "\\s*\\(.*\\)", "")) %>%
  select(concepticon_id, concepticon_gloss, semantic_field, ranklex_w, ranklex_i, rankmean_w, rankmean_r) %>%
  mutate(ranklex = (ranklex_w + ranklex_i) / 2,
         rankuse = (rankmean_w + rankmean_r) / 2) %>%
  mutate(concepticon_gloss = str_to_lower(concepticon_gloss))

hlhu <- both %>%
  filter(ranklex > 0.80, rankuse > 0.80)
  
top_20 <- both %>%
  arrange(desc(ranklex), concepticon_gloss) %>%
  filter(concepticon_id %in% hlhu$concepticon_id) %>%
  head(36) %>%
  select(concepticon_gloss) %>%
  mutate(concepticon_gloss = case_when(
    concepticon_gloss == "be alive or life" ~ "be alive",
    concepticon_gloss == "be dead or die" ~ "be dead",
    concepticon_gloss == "stone or rock" ~ "stone",
    concepticon_gloss == "center or middle" ~ "middle",
    concepticon_gloss == "strike or beat" ~ "beat",
    TRUE ~ concepticon_gloss
  )) %>% pull()

lllu <- both %>%
  filter(ranklex < 0.20, rankuse < 0.20)

bot_20 <- both %>%
  arrange(ranklex) %>%
  filter(concepticon_id %in% lllu$concepticon_id) %>%
  head(36) %>% 
  arrange(desc(ranklex), concepticon_gloss) %>%
  select(concepticon_gloss) %>%
  mutate(concepticon_gloss = case_when(
    concepticon_gloss == "flax or linen" ~ "linen",
    concepticon_gloss == "bronze or copper" ~ "bronze",
    concepticon_gloss == "sickle or scythe" ~ "sickle",
    TRUE ~ concepticon_gloss
  )) %>% 
  pull()

hllu <- both %>%
  filter(ranklex > 0.70, rankuse < 0.30)

highlex_20 <- both %>%
  arrange(desc(ranklex), concepticon_gloss) %>%
  filter(concepticon_id %in% hllu$concepticon_id) %>%
  head(36) %>% select(concepticon_gloss) %>%
  mutate(concepticon_gloss = case_when(
    concepticon_gloss == "upper leg" ~ "thigh",
    concepticon_gloss == "flax or linen" ~ "linen",
    concepticon_gloss == "crawl or creep" ~ "crawl",
    TRUE ~ concepticon_gloss
  ))  %>% pull()

llhu <- both %>%
  filter(ranklex < 0.35, rankuse > 0.65)

lowlex_20 <- both %>%
  arrange(ranklex) %>%
  filter(concepticon_id %in% llhu$concepticon_id) %>%
  head(36) %>% 
  arrange(desc(ranklex), concepticon_gloss) %>%
  select(concepticon_gloss) %>%
  mutate(concepticon_gloss = case_when(
    concepticon_gloss == "abstain from food" ~ "to fast",
    concepticon_gloss == "land" ~ "to land",
    concepticon_gloss == "marriage or wedding" ~ "marriage",
    concepticon_gloss == "nothing or zero" ~ "zero",
    concepticon_gloss == "allow or permit" ~ "allow",
    TRUE ~ concepticon_gloss
  )) %>% 
  pull()

format_words <- function(words, n_per_line = 4, bold_words = NULL) {

  split_words <- split(words, ceiling(seq_along(words) / n_per_line))

  formatted_words <- lapply(seq_along(split_words), function(i) {
    row_words <- split_words[[i]]

    row_words <- sapply(row_words, function(word) {
      if (!is.null(bold_words) && word %in% bold_words) {
        paste0("<b>", word, "</b>")
      } else {
        word
      }
    })
    
    if (i < length(split_words)) {
      row_words[length(row_words)] <- paste0(row_words[length(row_words)], ",")
    }
    
    paste(row_words, collapse = ", ")
  })

  paste(formatted_words, collapse = "<br>")
}

words_df <- data.frame(
  Usage = c("Low", "High", "Low", "High"),
  Lexicalization = c("High", "Low", "Low", "High"),
  words = c(
    format_words(highlex_20, bold_words = lists),
    format_words(lowlex_20, bold_words = lists),
    format_words(bot_20, bold_words = lists),
    format_words(top_20, bold_words = lists) 
  )
)

words_df$Usage <- factor(words_df$Usage, levels = c("Low", "High"))

concplot <- ggplot(words_df, aes(label = words)) +
  geom_richtext(aes(x = 0.5, y = 0.5),
                hjust = 0.5, vjust = 0.5, size = 1.97,
                fill = NA, label.color = NA) +
  facet_grid(Lexicalization ~ Usage) +
  theme_minimal(base_size = 9) +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    strip.background = element_blank(),
    strip.text = element_text(size = 7.875, face = "bold"),
    panel.spacing = unit(0.1, "lines"),
    panel.border = element_rect(color = "gray70", fill = NA, linewidth = 0.3),
    plot.margin = margin(1, 1, 1, 1)
  ) +
  xlab("Mean usage frequency") + ylab("Lexicalization score")

final_plot <- plot + concplot +
  plot_layout(ncol = 2, widths = c(1, 0.75), heights = c(1)) +
  plot_annotation(
    tag_levels = 'A',
    theme = theme(
      plot.tag = element_text(size = 7.875),
      plot.tag.position = c(0, 1)
    )
  )

ggsave(here("output/figures", "use_lex.pdf"), final_plot, width = 18, height = 7.875, units = "cm")
```

# Statistical analyses

Load data and standardize variables.

```{r load data, include=TRUE}
d_full <- read_csv(here("data", "d_full.csv"), show_col_types = FALSE) %>%
  mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.))) %>%
  mutate(across(wl_mean:sens, ~as.numeric(scale(.))))

d_dev <- read_csv(here("data", "d_dev.csv"), show_col_types = FALSE) %>%
  mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.))) %>%
  mutate(across(wl_mean:sens, ~as.numeric(scale(.))))
```

Let's look at correlation between predictor variables:

```{r}
# full set
predictors <- c(
  "wl_mean", "wl_cvar", "en",
  "do_mean", "do_cvar", "ins",
  "cd", "aoa_self", "conc", "sens"
)

pretty_names <- c(
  wl_mean  = "mean usage (Worldlex)",
  wl_cvar   = "CV of usage (Worldlex)",
  en       = "usage (English only)",
  do_mean  = "mean usage (DoReCo)",
  do_cvar   = "CV of usage (DoReCo)",
  ins      = "association in-strength",
  cd       = "contextual diversity",
  aoa_self = "AoA (self reported)",
  conc     = "concreteness",
  sens     = "sensorimotor strength"
)

# correlation matrix
cor_matrix <- d_full %>%
  select(all_of(predictors)) %>%
  cor(use = "pairwise.complete.obs")

rownames(cor_matrix) <- pretty_names[rownames(cor_matrix)]
colnames(cor_matrix) <- pretty_names[colnames(cor_matrix)]

cor_table <- round(cor_matrix, 2)
cor_table[lower.tri(cor_table)] <- NA

cor_df <- as.data.frame(cor_table, check.names = FALSE) %>%
  tibble::rownames_to_column(var = "predictor") %>%
  mutate(across(-predictor, ~ ifelse(is.na(.), "", sprintf("%.2f", .))))

colnames(cor_df)[1] <- ""

out_path <- here("output/tables", "pred_cor_full.tex")

print(
  xtable(cor_df, align = c("l", "l", rep("c", ncol(cor_df) - 1))),
  file = out_path,
  include.rownames = FALSE,
  sanitize.text.function = identity,
  comment = FALSE
)

# developmental set
predictors_dev <- c(
  "wl_mean", "wl_cvar", "en",
  "do_mean", "do_cvar", "ins",
  "cd", "aoa_self", "aoa_parent",
  "conc", "sens"
)

pretty_names <- c(
  wl_mean    = "mean usage (Worldlex)",
  wl_cvar     = "CV of usage (Worldlex)",
  en         = "usage (English only)",
  do_mean    = "mean usage (DoReCo)",
  do_cvar     = "CV of usage (DoReCo)",
  ins        = "association in-strength",
  cd         = "contextual diversity",
  aoa_self   = "AoA (self reported)",
  aoa_parent = "AoA (parent reported)",
  conc       = "concreteness",
  sens       = "sensorimotor strength"
)

cor_matrix_dev <- d_dev %>%
  select(all_of(predictors_dev)) %>%
  cor(use = "pairwise.complete.obs")

rownames(cor_matrix_dev) <- pretty_names[rownames(cor_matrix_dev)]
colnames(cor_matrix_dev) <- pretty_names[colnames(cor_matrix_dev)]

cor_table_dev <- round(cor_matrix_dev, 2)
cor_table_dev[lower.tri(cor_table_dev)] <- NA

cor_df_dev <- as.data.frame(cor_table_dev, check.names = FALSE) %>%
  tibble::rownames_to_column(var = "predictor") %>%
  mutate(across(-predictor, ~ ifelse(is.na(.), "", sprintf("%.2f", .))))
colnames(cor_df_dev)[1] <- ""

tab_dev <- xtable(
  cor_df_dev,
  align = c("l", "l", rep("c", ncol(cor_df_dev) - 1))
)

print(
  tab_dev,
  file = here("output/tables", "pred_cor_dev.tex"),
  include.rownames = FALSE,
  include.colnames = TRUE,
  sanitize.text.function = identity,
  floating = FALSE,
  comment = FALSE
)
```

## Frequentist analysis

Ordered beta regression analysis (frequentist):

```{r frequentist, include=TRUE}
run_glmm <- function(data, outcome_var, predictor_var) {
  
  fit_model_with_warnings <- function(formula) {
    warnings <- list()
    model <- withCallingHandlers(
      glmmTMB(formula, family = ordbeta(link = "logit"), data = data),
      warning = function(w) {
        warnings <<- c(warnings, w$message)
        invokeRestart("muffleWarning")
      }
    )
    list(model = model, warnings = warnings)
  }
  
  formula_full <- as.formula(paste(outcome_var, "~", predictor_var))
  formula_null <- as.formula(paste(outcome_var, "~ 1"))
  
  full_fit <- fit_model_with_warnings(formula_full)
  
  if (predictor_var == "1") {
    
    summ <- tibble(
      outcome = outcome_var,
      predictor = predictor_var,
      BIC = BIC(full_fit$model),
      AIC = AIC(full_fit$model),
      term = "(Intercept)",
      estimate = fixef(full_fit$model)$cond["(Intercept)"],
      conf.low = NA_real_,
      conf.high = NA_real_,
      chisq = NA_real_,
      df = NA_real_,
      p.value = NA_real_,
      warnings = if (length(full_fit$warnings) > 0) paste(full_fit$warnings, collapse = ";") else ""
    )
    
  } else {
    
    null_fit <- fit_model_with_warnings(formula_null)
    aov_result <- anova(null_fit$model, full_fit$model)
    
    chisq_val <- aov_result$Chisq[2]
    df_val <- aov_result$`Chi Df`[2]
    p_val <- aov_result$`Pr(>Chisq)`[2]
    
    coefs <- tidy(full_fit$model) %>%
      filter(component == "cond", term != "(Intercept)")

    ci <- confint(full_fit$model, component = "cond", level = 0.95)

    ci_cond <- as.data.frame(ci) %>%
      tibble::rownames_to_column("term") %>%
      rename(
       conf.low = `2.5 %`,
       conf.high = `97.5 %`
      )

    coefs <- coefs %>%
      left_join(ci_cond, by = "term")
    
    pred_terms <- attr(terms(formula_full), "term.labels")
    
    me <- tryCatch(
      suppressMessages(
        suppressWarnings(
          avg_slopes(
            full_fit$model,
            variables = pred_terms
          ) %>%
            as.data.frame()
        )
      ),
      error = function(e) NULL
    )
    
    summ <- tibble(
      outcome = outcome_var,
      predictor = predictor_var,
      BIC = BIC(full_fit$model),
      AIC = AIC(full_fit$model),
      term = coefs$term,
      estimate = coefs$estimate,
      conf.low = coefs$conf.low,
      conf.high = coefs$conf.high,
      chisq = chisq_val,
      df = df_val,
      p.value = p_val,
      warnings = if (length(full_fit$warnings) > 0) paste(full_fit$warnings, collapse = ";") else ""
    )
  }
  
  return(summ)
}

# full set
outcome_vars <- c("lex_wold", "lex_ids")
predictors_full <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "cd", "conc", "sens", "ins", "1")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_full) {
    result <- run_glmm(data = d_full, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_full <- bind_rows(results_list) 

# developmental set
predictors_dev <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "aoa_parent", "cd", "conc", "sens", "ins", "1")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_dev) {
    result <- run_glmm(data = d_dev, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_dev <- bind_rows(results_list)
```

Make table:

```{r main table 1 and 2, include=TRUE}

make_table <- function(data) {
  
  table <- data %>%
    select(-warnings) %>%
    mutate(type = case_when(
      predictor == "1" ~ "null",
      predictor %in% c("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean", "en") ~ "frequency",
      TRUE ~ "other"
    )) %>%
    group_by(outcome) %>%
    mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
    ungroup() %>%
    select(-shiftbic, -shiftaic) %>%
    mutate(predictor = case_when(
      predictor == "aoa_self" ~ "AoA (self reported)",
      predictor == "aoa_parent" ~ "AoA (parent reported)",
      predictor == "wl_mean + wl_cvar" ~ "mean + CV (Worldlex)",
      predictor == "wl_mean" ~ "mean usage (Worldlex)",
      predictor == "ins" ~ "association in-strength",
      predictor == "en" ~ "usage (English only)",
      predictor == "cd" ~ "contextual diversity",
      predictor == "1" ~ "null model",
      predictor == "do_mean" ~ "mean usage (DoReCo)",
      predictor == "do_mean + do_cvar" ~ "mean + CV (DoReCo)",
      predictor == "conc" ~ "concreteness",
      predictor == "sens" ~ "sensorimotor strength",
      TRUE ~ predictor
    )) %>%
    rename(variable = term) %>%
    mutate(variable = case_when(
      variable == "(Intercept)" ~ "intercept",
      predictor == "mean + CV (Worldlex)" & variable == "wl_mean" ~ "mean",
      predictor == "mean + CV (Worldlex)" & variable == "wl_cvar" ~ "CV",
      predictor == "mean + CV (DoReCo)" & variable == "do_mean" ~ "mean",
      predictor == "mean + CV (DoReCo)" & variable == "do_cvar" ~ "CV",
      TRUE ~ NA
    )) %>%
    mutate(p.value = case_when(
    p.value < 0.001 ~ as.character('< 0.001'),
    TRUE ~ sprintf("%.3f", p.value))) %>%
    mutate(lower_ci = sprintf("%.2f", conf.low),
      upper_ci = sprintf("%.2f", conf.high),
      ci = paste0("[", lower_ci, ", ", upper_ci, "]")) %>%
    arrange(BIC) 
  
  return(table)
  
}
  
wold_full_tab <- f_full %>%
  filter(outcome == "lex_wold") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

ids_full_tab <- f_full %>%
  filter(outcome == "lex_ids") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

t_full <- bind_rows(ids_full_tab, wold_full_tab) %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

full_table <- xtable(t_full, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(full_table, file = here("output", "tables", "freq_full.tex"), include.rownames = FALSE, comment = FALSE)

wold_dev_tab <- f_dev %>%
  filter(outcome == "lex_wold") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

ids_dev_tab <- f_dev %>%
  filter(outcome == "lex_ids") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

t_dev <- bind_rows(ids_dev_tab, wold_dev_tab)  %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

dev_table <- xtable(t_dev,  digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(dev_table, file = here("output", "tables", "freq_dev.tex"), include.rownames = FALSE, comment = FALSE)
```

## Comparison between models with multiple predictors

Compare between models with all other predictors and models with all predictors including frequency variables:

```{r}
# full set
predictors_full_all <- list(
                   "aoa_self + cd + conc + sens + ins",
                   "aoa_self + cd + conc + sens + ins + wl_mean",
                   "aoa_self + cd + conc + sens + ins + do_mean",
                   "aoa_self + cd + conc + sens + ins + en",
                   "aoa_self + cd + conc + sens + ins + wl_mean + wl_cvar",
                   "aoa_self + cd + conc + sens + ins + do_mean + do_cvar")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_full_all) {
    result <- run_glmm(data = d_full, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_full_all <- bind_rows(results_list) 

# developmental set
predictors_dev_all <- list("aoa_self + aoa_parent + cd + conc + sens + ins",
                           "aoa_self + aoa_parent + cd + conc + sens + ins + wl_mean",
                           "aoa_self + aoa_parent + cd + conc + sens + ins + do_mean",
                           "aoa_self + aoa_parent + cd + conc + sens + ins + en",
                           "aoa_self + aoa_parent + cd + conc + sens + ins + wl_mean + wl_cvar",
                           "aoa_self + aoa_parent + cd + conc + sens + ins + do_mean + do_cvar")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_dev_all) {
    result <- run_glmm(data = d_dev, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_dev_all <- bind_rows(results_list)
```

Compare between models with another predictor only and models with another predictor plus a frequency predictor

```{r}
# full set
predictors_full_combo <- list("aoa_self", "cd", "conc", "sens", "ins",
"aoa_self + wl_mean", "cd + wl_mean", "conc + wl_mean", "sens + wl_mean", "ins + wl_mean",
"aoa_self + do_mean", "cd + do_mean", "conc + do_mean", "sens + do_mean", "ins + do_mean",
"aoa_self + en", "cd + en", "conc + en", "sens + en", "ins + en",
"aoa_self + wl_mean + wl_cvar", "cd + wl_mean + wl_cvar", "conc + wl_mean + wl_cvar", "sens + wl_mean + wl_cvar", "ins + wl_mean + wl_cvar",
"aoa_self + do_mean + do_cvar", "cd + do_mean + do_cvar", "conc + do_mean + do_cvar", "sens + do_mean + do_cvar", "ins + do_mean + do_cvar")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_full_combo) {
    result <- run_glmm(data = d_full, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_full_combo <- bind_rows(results_list) 

# developmental set
predictors_dev_combo <- list("aoa_self", "cd", "conc", "sens", "ins", "aoa_parent", 
"aoa_self + wl_mean", "cd + wl_mean", "conc + wl_mean", "sens + wl_mean", "ins + wl_mean","aoa_parent + wl_mean", 
"aoa_self + do_mean", "cd + do_mean", "conc + do_mean", "sens + do_mean", "ins + do_mean","aoa_parent + do_mean", 
"aoa_self + en", "cd + en", "conc + en", "sens + en", "ins + en","aoa_parent + en", 
"aoa_self + wl_mean + wl_cvar", "cd + wl_mean + wl_cvar", "conc + wl_mean + wl_cvar", "sens + wl_mean + wl_cvar", "ins + wl_mean + wl_cvar","aoa_parent + wl_mean + wl_cvar", 
"aoa_self + do_mean + do_cvar", "cd + do_mean + do_cvar", "conc + do_mean + do_cvar", "sens + do_mean + do_cvar", "ins + do_mean + do_cvar","aoa_parent + do_mean + do_cvar")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_dev_combo) {
    result <- run_glmm(data = d_dev, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_dev_combo <- bind_rows(results_list) 
```

Compare all models:

```{r}
all_full <- bind_rows(f_full, f_full_all, f_full_combo) %>% 
  distinct(outcome, predictor, BIC, AIC) %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)

all_dev <- bind_rows(f_dev, f_dev_all, f_dev_combo) %>% 
  distinct(outcome, predictor, BIC, AIC)  %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)
```

Make tables for all predictor comparison:

```{r}
f_full_all <- f_full_all %>% 
  distinct(outcome, predictor, BIC, AIC) %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)

rename_predictors <- c(
  "wl_mean" = "mean usage (Worldlex)",
  "wl_cvar" = "CV of usage (Worldlex)",
  "do_mean" = "mean usage (DoReCo)",
  "do_cvar" = "CV of usage (DoReCo)",
  "aoa_self + cd + conc + sens + ins" = "all other predictors",
  "en" = "usage (English only)"
)

f_full_all_tbl <- reduce(
  names(rename_predictors),
  .init = f_full_all,
  .f = function(df, pat) {
    df %>%
      mutate(
        predictor = str_replace_all(
          predictor,
          fixed(pat),
          rename_predictors[[pat]]
        )
      )
  }
) 

f_dev_all <- f_dev_all %>% 
  distinct(outcome, predictor, BIC, AIC) %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)

rename_predictors <- c(
  "wl_mean" = "mean usage (Worldlex)",
  "wl_cvar" = "CV of usage (Worldlex)",
  "do_mean" = "mean usage (DoReCo)",
  "do_cvar" = "CV of usage (DoReCo)",
  "aoa_self + aoa_parent + cd + conc + sens + ins" = "all other predictors",
  "en" = "usage (English only)"
)

f_dev_all_tbl <- reduce(
  names(rename_predictors),
  .init = f_dev_all,
  .f = function(df, pat) {
    df %>%
      mutate(
        predictor = str_replace_all(
          predictor,
          fixed(pat),
          rename_predictors[[pat]]
        )
      )
  }
)

f_all_tbl <- bind_rows(f_full_all_tbl, f_dev_all_tbl)

all_table <- xtable(f_all_tbl, digits = c(0, 0,  0, 0, 0))
print(all_table, file = here("output", "tables", "model_comparison_all.tex"), include.rownames = FALSE, comment = FALSE)

```

Make tables for pair comparison:

```{r}
f_full_combo <- f_full_combo %>% 
  distinct(outcome, predictor, BIC, AIC) %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)

usage_terms <- c("do_mean", "do_cvar", "wl_mean", "wl_cvar", "en")

f_full_combo2 <- f_full_combo %>%
  mutate(
    type = predictor %>%
      str_split(" \\+ ") %>%
      sapply(function(x) {
        paste(setdiff(x, usage_terms), collapse = " + ")
      })
  )  %>%
  arrange(BIC)  %>%
  arrange(type) %>%
  arrange(outcome)

rename_predictors <- c(
  "aoa_self" = "AoA (self reported)",
  "aoa_parent" = "AoA (parent reported)",
  "wl_mean" = "mean usage (Worldlex)",
  "wl_cvar" = "CV of usage (Worldlex)",
  "do_mean" = "mean usage (DoReCo)",
  "do_cvar" = "CV of usage (DoReCo)",
  "ins" = "association in-strength",
  "en" = "usage (English only)",
  "cd" = "contextual diversity",
  "conc" = "concreteness",
  "sens" = "sensorimotor strength"
)

f_full_combo_tbl <- f_full_combo2 %>%
  mutate(
    predictor = map_chr(str_split(predictor, " \\+ "), function(x) {
      x <- ifelse(x %in% names(rename_predictors), rename_predictors[x], x)
      paste(x, collapse = " + ")
    }),
    type = ifelse(type %in% names(rename_predictors), rename_predictors[type], type)
  ) %>%
  select(-type)

table1 <- f_full_combo_tbl %>%
  filter(outcome == "lex_ids") %>%
  select(-outcome)
combo_table <- xtable(table1, digits = c(0, 0, 0, 0))
print(combo_table, file = here("output", "tables", "model_comparison_pairs_ids.tex"), include.rownames = FALSE, comment = FALSE)

table2 <- f_full_combo_tbl %>%
  filter(outcome == "lex_wold") %>%
  select(-outcome)
combo_table2 <- xtable(table2, digits = c(0, 0, 0, 0))
print(combo_table2, file = here("output", "tables", "model_comparison_pairs_wold.tex"), include.rownames = FALSE, comment = FALSE)

f_dev_combo <- f_dev_combo %>% 
  distinct(outcome, predictor, BIC, AIC) %>%
  group_by(outcome) %>%
  mutate(shiftbic = min(BIC, na.rm=TRUE),
           shiftaic = min(AIC, na.rm=TRUE),
           BIC = BIC - shiftbic,
           AIC = AIC - shiftaic) %>%
  ungroup() %>%
  select(-shiftbic, -shiftaic) %>%
  arrange(BIC) %>%
  arrange(outcome)

f_dev_combo2 <- f_dev_combo %>%
  mutate(
    type = predictor %>%
      str_split(" \\+ ") %>%
      sapply(function(x) {
        paste(setdiff(x, usage_terms), collapse = " + ")
      })
  )  %>%
  arrange(BIC)  %>%
  arrange(type) %>%
  arrange(outcome)

f_dev_combo_tbl <- f_dev_combo2 %>%
  mutate(
    predictor = map_chr(str_split(predictor, " \\+ "), function(x) {
      x <- ifelse(x %in% names(rename_predictors), rename_predictors[x], x)
      paste(x, collapse = " + ")
    }),
    type = ifelse(type %in% names(rename_predictors), rename_predictors[type], type)
  ) %>%
  select(-type)

table1 <- f_dev_combo_tbl %>%
  filter(outcome == "lex_ids") %>%
  select(-outcome)
combo_table <- xtable(table1, digits = c(0, 0, 0, 0))
print(combo_table, file = here("output", "tables", "model_comparison_pairs_ids_dev.tex"), include.rownames = FALSE, comment = FALSE)

table2 <- f_dev_combo_tbl %>%
  filter(outcome == "lex_wold") %>%
  select(-outcome)
combo_table2 <- xtable(table2, digits = c(0, 0, 0, 0))
print(combo_table2, file = here("output", "tables", "model_comparison_pairs_wold_dev.tex"), include.rownames = FALSE, comment = FALSE)
```

## Analysis on strict set

Load data and standardize variables.

```{r load data, include=TRUE}
d_full_strict <- read_csv(here("data", "d_full_strict.csv"), show_col_types = FALSE) %>%
  mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.))) %>%
  mutate(across(wl_mean:sens, ~as.numeric(scale(.))))

d_dev_strict <- read_csv(here("data", "d_dev_strict.csv"), show_col_types = FALSE) %>%
  mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.))) %>%
  mutate(across(wl_mean:sens, ~as.numeric(scale(.))))
```

Run frequentist analyses

```{r}
# full set
outcome_vars <- c("lex_wold_strict")
predictors_full <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "cd", "conc", "sens", "ins", "1")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_full) {
    result <- run_glmm(data = d_full_strict, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_full_strict <- bind_rows(results_list) 

# developmental set
predictors_dev <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "aoa_parent", "cd", "conc", "sens", "ins", "1")

results_list <- list()
for (outcome in outcome_vars) {
  for (predictor in predictors_dev) {
    result <- run_glmm(data = d_dev_strict, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}
f_dev_strict <- bind_rows(results_list)

```

Make table:

```{r}
wold_full_strict <- f_full_strict %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

wold_dev_strict <- f_dev_strict %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

t_full_strict <- bind_rows(wold_full_strict, wold_dev_strict) %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

full_table <- xtable(t_full_strict, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(full_table, file = here("output", "tables", "freq_strict.tex"), include.rownames = FALSE, comment = FALSE)
```

## Bayesian analysis

Ordered beta regression analysis (Bayesian):

```{r bayesian, include=TRUE, eval=FALSE}

set.seed(123)

quiet_ordbrm <- quietly(ordbetareg)

run_bayes_ord <- function(data, outcome_var, predictor_var) {
  
  formula <- as.formula(paste(outcome_var, "~", predictor_var))
  
  mdl <- quiet_ordbrm(
    formula = formula,
    data = data,
    chains = 4,
    iter = 2000,
    warmup = 1000,
    cores = 4,
    seed = 123,
    control = list(adapt_delta = 0.95, stepsize = 0.01, max_treedepth = 15)
  )
  
  m <- mdl$result
  loo_res <- loo(m)
  coef_summary <- fixef(m)
  
  if (predictor_var == "0 + Intercept") {
    
    target_coefs <- coef_summary["Intercept", , drop = FALSE]
    
    summ <- tibble(
      outcome = outcome_var,
      predictor = predictor_var,
      term = "Intercept",
      coefficient = target_coefs[, 1],
      lower_ci = target_coefs[, 3],
      upper_ci = target_coefs[, 4],
      loo_elpd = loo_res$estimates["elpd_loo", "Estimate"],
      loo_se = loo_res$estimates["elpd_loo", "SE"],
      warnings = paste(mdl$warnings, collapse = " | "),
      marginal_effect = NA_real_,
      conf_low = NA_real_,
      conf_high = NA_real_
    )
    
  } else {
    
    pred_terms <- attr(terms(formula), "term.labels")
    
    coef_df <- as.data.frame(coef_summary) %>%
      tibble::rownames_to_column("term") %>%
      filter(term %in% pred_terms) %>%
      transmute(
        term,
        coefficient = Estimate,
        lower_ci = Q2.5,
        upper_ci = Q97.5
      )
    
    me <- tryCatch(
      suppressMessages(
        suppressWarnings(
          avg_slopes(
            m,
            variables = pred_terms,
            re.form = NA
          ) %>%
            as.data.frame()
        )
      ),
      error = function(e) NULL
    )
    
    if (!is.null(me)) {
      me <- me %>%
        select(term, estimate, conf.low, conf.high) %>%
        rename(
          marginal_effect = estimate,
          conf_low = conf.low,
          conf_high = conf.high
        )
      
      coef_df <- coef_df %>%
        left_join(me, by = "term")
    } else {
      coef_df <- coef_df %>%
        mutate(
          marginal_effect = NA_real_,
          conf_low = NA_real_,
          conf_high = NA_real_
        )
    }
    
    summ <- coef_df %>%
      mutate(
        outcome = outcome_var,
        predictor = predictor_var,
        loo_elpd = loo_res$estimates["elpd_loo", "Estimate"],
        loo_se = loo_res$estimates["elpd_loo", "SE"],
        warnings = paste(mdl$warnings, collapse = " | ")
      ) %>%
      select(
        outcome, predictor, term, coefficient, lower_ci, upper_ci,
        loo_elpd, loo_se, warnings,
        marginal_effect, conf_low, conf_high
      )
  }
  
  return(summ)
}

# full set
outcome_vars <- c("lex_wold", "lex_ids")
predictors <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "cd", "conc", "sens", "ins", "0 + Intercept")

results_list <- list()

for (outcome in outcome_vars) {
  for (predictor in predictors) {
    result <- run_bayes_ord(data = d_full, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}

b_full <- bind_rows(results_list) %>%
  write_csv(here("output/results", "bayes_full.csv"))

# developmental set
predictors <- list("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean",
                   "en", "aoa_self", "aoa_parent", "cd", "conc", "sens", "ins", "0 + Intercept")

results_list <- list()

for (outcome in outcome_vars) {
  for (predictor in predictors) {
    result <- run_bayes_ord(data = d_dev, outcome_var = outcome, predictor_var = predictor)
    results_list <- append(results_list, list(result))
  }
}

b_dev <- bind_rows(results_list) %>%
  write_csv(here("output/results", "bayes_dev.csv"))
```

Make tables:

```{r supp table 1, include=TRUE, eval=FALSE}
b_full <- read_csv(here("output/results", "bayes_full.csv"), show_col_types = FALSE)
b_dev <- read_csv(here("output/results", "bayes_dev.csv"), show_col_types = FALSE)

make_table_bayes <- function(data) {
  
  table <- data %>%
    select(-loo_se, -warnings) %>%
    mutate(type = case_when(
      predictor == "0 + Intercept" ~ "null",
      predictor %in% c("wl_mean + wl_cvar", "wl_mean", "do_mean + do_cvar", "do_mean", "en") ~ "frequency",
      TRUE ~ "other"
    )) %>%
    group_by(outcome) %>%
    mutate(shiftelpd = max(loo_elpd, na.rm=TRUE),
           elpd = loo_elpd - shiftelpd) %>%
    ungroup() %>%
    select(-shiftelpd, -loo_elpd) %>%
    mutate(predictor = case_when(
      predictor == "aoa_self" ~ "AoA (self reported)",
      predictor == "aoa_parent" ~ "AoA (parent reported)",
      predictor == "wl_mean + wl_cvar" ~ "mean + CV (Worldlex)",
      predictor == "wl_mean" ~ "mean usage (Worldlex)",
      predictor == "ins" ~ "association in-strength",
      predictor == "en" ~ "usage (English only)",
      predictor == "cd" ~ "contextual diversity",
      predictor == "0 + Intercept" ~ "null model",
      predictor == "do_mean" ~ "mean usage (DoReCo)",
      predictor == "do_mean + do_cvar" ~ "mean + CV (DoReCo)",
      predictor == "conc" ~ "concreteness",
      predictor == "sens" ~ "sensorimotor strength",
      TRUE ~ predictor
    )) %>%
    mutate(term = case_when(
      predictor == "mean + CV (Worldlex)" & term == "wl_mean" ~ "mean",
      predictor == "mean + CV (Worldlex)" & term == "wl_cvar" ~ "CV",
      predictor == "mean + CV (DoReCo)" & term == "do_mean" ~ "mean",
      predictor == "mean + CV (DoReCo)" & term == "do_cvar" ~ "CV",
      TRUE ~ NA
    )) %>%
    mutate(
      lower_ci = sprintf("%.2f", lower_ci),
      upper_ci = sprintf("%.2f", upper_ci),
      ci = paste0("[", lower_ci, ", ", upper_ci, "]"),
      conf_low = sprintf("%.2f", conf_low),
      conf_high = sprintf("%.2f", conf_high),
      ci_me = paste0("[", conf_low, ", ", conf_high, "]")
    )
  
  return(table)
  
}

bt_wold_full <- make_table_bayes(b_full) %>%
  filter(outcome == "lex_wold") %>%
  rename(coef = coefficient, me = marginal_effect, cime = ci_me) %>%
  select(type, predictor, term, elpd, coef, ci, me, cime)  %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(desc(elpd)) %>%
  arrange(type) %>%
  select(-type)
  
bt_ids_full <- make_table_bayes(b_full) %>%
  filter(outcome == "lex_ids") %>%
  rename(coef = coefficient, me = marginal_effect, cime = ci_me) %>%
  select(type, predictor, term, elpd, coef, ci, me, cime)   %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(desc(elpd)) %>%
  arrange(type) %>%
  select(-type)

bt_full <- bind_rows(bt_ids_full, bt_wold_full)

t_table <- xtable(bt_full, digits = c(0, 0, 0, 0, 2, 0, 2, 0))
print(t_table, file = here("output", "tables", "bayes_full.tex"), include.rownames = FALSE, comment = FALSE)

bt_wold_dev <- make_table_bayes(b_dev) %>%
  filter(outcome == "lex_wold") %>%
  rename(coef = coefficient, me = marginal_effect, cime = ci_me) %>%
  select(type, predictor, term, elpd, coef, ci, me, cime)  %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(desc(elpd)) %>%
  arrange(type) %>%
  select(-type)
  
bt_ids_dev <- make_table_bayes(b_dev) %>%
  filter(outcome == "lex_ids") %>%
  rename(coef = coefficient, me = marginal_effect, cime = ci_me) %>%
  select(type, predictor, term, elpd, coef, ci, me, cime)  %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(desc(elpd)) %>%
  arrange(type) %>%
  select(-type)

bt_dev <- bind_rows(bt_ids_dev, bt_wold_dev)
t_table <- xtable(bt_dev, digits = c(0, 0, 0, 0, 2, 0, 2, 0))
print(t_table, file = here("output", "tables", "bayes_dev.tex"), include.rownames = FALSE, comment = FALSE)

```

## Logistic regression with macro area

Load lexicalization data:

```{r}
wold <- read_csv(here("data", "wold_data.csv"), show_col_types = FALSE)
ids <- read_csv(here("data", "ids_data.csv"), show_col_types = FALSE) 

wold_full <- wold %>%
  inner_join(d_full %>% select(concepticon_id, ontological_category, semantic_category, wl_mean:sens), by = "concepticon_id")
wold_dev <- wold %>%
  inner_join(d_dev %>% select(concepticon_id, ontological_category, semantic_category,  wl_mean:sens), by = "concepticon_id")

ids_full <- ids %>%
  inner_join(d_full %>% select(concepticon_id, ontological_category, semantic_category,  wl_mean:sens), by = "concepticon_id")
ids_dev <- ids %>%
  inner_join(d_dev %>% select(concepticon_id, ontological_category, semantic_category,  wl_mean:sens), by = "concepticon_id")
```

We run frequentist logistic regression analysis:

```{r, eval=FALSE}
run_freq_logistic <- function(data, predictor_var, dataset_name) {

  fit_model_with_warnings <- function(formula) {
    warnings <- list()
    model <- withCallingHandlers(
      glmmTMB(formula, family = binomial(link = "logit"), data = data),
      warning = function(w) {
        warnings <<- c(warnings, w$message)
        invokeRestart("muffleWarning")
      }
    )
    if (any(str_detect(warnings, "non-positive-definite"))) {
      message("Retrying with BFGS optimizer...")
      warnings <- list()
      model <- withCallingHandlers(
        glmmTMB(formula, family = binomial(link = "logit"), data = data,
                control = glmmTMBControl(optimizer = optim,
                                         optArgs = list(method = "BFGS"))),
        warning = function(w) {
          warnings <<- c(warnings, w$message)
          invokeRestart("muffleWarning")
        }
      )
    }
    list(model = model, warnings = warnings)
  }

  formula_full <- as.formula(
    paste("lex ~", predictor_var,
          "+ (1 | concepticon_id) + (1 | glottocode) + (1 | family) + (1 | area)")
  )
  formula_null <- as.formula(
    "lex ~ 1 + (1 | concepticon_id) + (1 | glottocode) + (1 | family) + (1 | area)"
  )

  full_fit <- fit_model_with_warnings(formula_full)

  if (predictor_var == "1") {

    summ <- tibble(
      outcome   = dataset_name,
      predictor = predictor_var,
      BIC       = BIC(full_fit$model),
      AIC       = AIC(full_fit$model),
      term      = "(Intercept)",
      estimate  = fixef(full_fit$model)$cond["(Intercept)"],
      conf.low  = NA_real_,
      conf.high = NA_real_,
      chisq     = NA_real_,
      df        = NA_real_,
      p.value   = NA_real_,
      warnings  = if (length(full_fit$warnings) > 0) paste(full_fit$warnings, collapse = ";") else ""
    )

  } else {

    null_fit   <- fit_model_with_warnings(formula_null)
    aov_result <- anova(null_fit$model, full_fit$model)

    chisq_val <- aov_result$Chisq[2]
    df_val    <- aov_result$`Chi Df`[2]
    p_val     <- aov_result$`Pr(>Chisq)`[2]

    coefs <- tidy(full_fit$model) |>
      filter(component == "cond", term != "(Intercept)", !str_detect(term, "^sd__"))

    ci <- confint(full_fit$model, component = "cond", level = 0.95)

    ci_cond <- as.data.frame(ci) |>
      tibble::rownames_to_column("term") |>
      rename(conf.low = `2.5 %`, conf.high = `97.5 %`)

    coefs <- coefs |> left_join(ci_cond, by = "term")

    summ <- tibble(
      outcome   = dataset_name,
      predictor = predictor_var,
      BIC       = BIC(full_fit$model),
      AIC       = AIC(full_fit$model),
      term      = coefs$term,
      estimate  = coefs$estimate,
      conf.low  = coefs$conf.low,
      conf.high = coefs$conf.high,
      chisq     = chisq_val,
      df        = df_val,
      p.value   = p_val,
      warnings  = if (length(full_fit$warnings) > 0) paste(full_fit$warnings, collapse = ";") else ""
    )
  }

  return(summ)
}

f_full_log <- bind_rows(
  map(predictors_full, ~ run_freq_logistic(wold_full, .x, "wold_full")),
  map(predictors_full, ~ run_freq_logistic(ids_full,  .x, "ids_full"))
) %>% write_csv(here("output", "results", "freq_log_full.csv"))

f_dev_log <- bind_rows(
  map(predictors_dev, ~ run_freq_logistic(wold_dev, .x, "wold_dev")),
  map(predictors_dev, ~ run_freq_logistic(ids_dev,  .x, "ids_dev"))
) %>% write_csv(here("output", "results", "freq_log_dev.csv"))
```

Now make a table:

```{r}
f_full_log <- read_csv(here("output", "results", "freq_log_full.csv"))
f_dev_log <- read_csv(here("output", "results", "freq_log_dev.csv"))

wold_full_log <- f_full_log %>%
  filter(outcome == "wold_full") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)
  
ids_full_log <- f_full_log %>%
  filter(outcome == "ids_full") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

t_full_log <- bind_rows(ids_full_log, wold_full_log) %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

full_table <- xtable(t_full_log, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(full_table, file = here("output", "tables", "freq_full_log.tex"), include.rownames = FALSE, comment = FALSE)

wold_dev_log <- f_dev_log %>%
  filter(outcome == "wold_dev") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)
  
ids_dev_log <- f_dev_log %>%
  filter(outcome == "ids_dev") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

t_dev_log <- bind_rows(ids_dev_log, wold_dev_log)  %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

dev_table <- xtable(t_dev_log,  digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(dev_table, file = here("output", "tables", "freq_dev_log.tex"), include.rownames = FALSE, comment = FALSE)
```

## Noun vs. Verb

```{r nouns frequentist, include=TRUE}

d_full <- read_csv(here("data", "d_full.csv"), show_col_types = FALSE)

d_dev <- read_csv(here("data", "d_dev.csv"), show_col_types = FALSE)

run_glmm_for_category <- function(data, categories, outcome_vars, predictors) {
  
  data_filtered <- data %>% 
    filter(semantic_category %in% categories)   %>%
    mutate(across(c(wl_mean, wl_cvar, en, do_mean, do_cvar, cd), ~ log(.))) %>%
    mutate(across(wl_mean:sens, ~as.numeric(scale(.))))
    
  
  results_list <- list()
  
  for (outcome in outcome_vars) {
    for (predictor in predictors) {
      result <- run_glmm(data = data_filtered, outcome_var = outcome, predictor_var = predictor)
      results_list <- append(results_list, list(result))
    }
  }
  
  bind_rows(results_list)

}

outcome_vars <- c("lex_wold", "lex_ids")

# Full set
f_full_n <- run_glmm_for_category(d_full, c("Noun"), outcome_vars, predictors_full)
f_full_v <- run_glmm_for_category(d_full, c("Verb"), outcome_vars, predictors_full)

# Developmental set
f_dev_n <- run_glmm_for_category(d_dev, c("Noun"), outcome_vars, predictors_dev)
f_dev_v <- run_glmm_for_category(d_dev, c("Verb"), outcome_vars, predictors_dev)

```

Make table:

```{r supp table 6 & 7, include=TRUE}

combine_table <- function(my_data){

ids <- my_data %>%
  filter(outcome == "lex_ids") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)

wold <- my_data %>%
  filter(outcome == "lex_wold") %>%
  make_table() %>%
  mutate(type = factor(type, levels = c("null", "frequency", "other"))) %>%
  arrange(BIC) %>%
  arrange(type)
  
t <- bind_rows(ids, wold) %>%
  select(predictor, variable, BIC, AIC, estimate, ci, chisq, df, p.value)

return(t)
}

t_full_n <- combine_table(f_full_n)
t_table <- xtable(t_full_n, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(t_table, file = here("output", "tables", "noun_full.tex"), include.rownames = FALSE, comment = FALSE)

t_dev_n <- combine_table(f_dev_n)
t_table <- xtable(t_dev_n, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(t_table, file = here("output", "tables", "noun_dev.tex"), include.rownames = FALSE, comment = FALSE)

t_full_v <- combine_table(f_full_v)
t_table <- xtable(t_full_v, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(t_table, file = here("output", "tables", "verb_full.tex"), include.rownames = FALSE, comment = FALSE)

t_dev_v <- combine_table(f_dev_v)
t_table <- xtable(t_dev_v, digits = c(0, 0, 0, 0, 0, 2, 0, 2, 0, 0))
print(t_table, file = here("output", "tables", "verb_dev.tex"), include.rownames = FALSE, comment = FALSE)

```

Make figure:

```{r supp fig 3, include=TRUE}

set.seed(130)

make_fig <- function(data1, data2, var) {

d <- data1 %>%
  filter(outcome == {{var}}) %>%
  select(outcome, predictor, BIC) %>%
  rename(bic_n = BIC) %>%
  left_join(data2 %>%
  filter(outcome == {{var}}) %>%
  select(outcome, predictor, BIC) %>%
  rename(bic_v = BIC), by = c("outcome", "predictor"),
  relationship = "many-to-many") %>%
  unique() %>%
  mutate(across(c(bic_n, bic_v), ~rescale(.x, to = c(0, 100))))

d_long <- d %>%
  pivot_longer(cols = c(bic_n, bic_v), 
               names_to = "type", 
               values_to = "bic") %>%
  mutate(type = recode(type, bic_n = "Noun", bic_v = "Verb")) %>%
  mutate(tag = case_when(
    predictor == "wl_mean + wl_cvar" ~ "frequency of use",
    predictor == "wl_mean" ~ "frequency of use",
    predictor == "do_mean + do_cvar" ~ "frequency of use",
    predictor == "do_mean" ~ "frequency of use",
    predictor == "en" ~ "frequency of use",
    predictor == "sens" ~ "sensorimotor",
    predictor == "conc" ~ "concreteness",
    predictor == "cd" ~ "contextual diversity",
    predictor == "ins" ~ "association in-strength",
    predictor == "aoa_self" ~ "age-of-acquisition",
    predictor == "aoa_parent" ~ "age-of-acquisition",
    predictor == "1" ~ "null"
  )) %>%
    mutate(predictor = case_when(
      predictor == "aoa_self" ~ "AoA (self reported)",
      predictor == "aoa_parent" ~ "AoA (parent reported)",
      predictor == "wl_mean + wl_cvar" ~ "mean + CV (Worldlex)",
      predictor == "wl_mean" ~ "mean usage (Worldlex)",
      predictor == "ins" ~ "association in-strength",
      predictor == "en" ~ "usage (English only)",
      predictor == "cd" ~ "contextual diversity",
      predictor == "1" ~ "null model",
      predictor == "do_mean" ~ "mean usage (DoReCo)",
      predictor == "do_mean + do_cvar" ~ "mean + CV (DoReCo)",
      predictor == "conc" ~ "concreteness",
      predictor == "sens" ~ "sensorimotor strength",
      TRUE ~ predictor
    )) 

d_labels <- d_long %>% filter(type == "Verb")

p <- ggplot(d_long, aes(x = type, y = bic, group = predictor, color = tag)) +
    geom_point(size = 0.5) +
    geom_line(size = 0.2) +
    geom_text_repel(
      data = d_labels,
      aes(label = predictor),
      size = 2.8125,
      nudge_x = 1,
      direction = "y",
      hjust = 0,
      segment.size = 0.2,
      show.legend = FALSE,
      force = 30,
      force_pull = 0.5,
      max.iter = 20000,
      max.time = 2,
      box.padding = 0.2,
      max.overlaps = Inf
    ) +
  scale_color_manual(values = c(
    "frequency of use" = "#1b9e77",
    "sensorimotor" = "#d95f02",
    "concreteness" = "#7570b3",
    "contextual diversity" = "#66a61e",
    "association in-strength" = "#e6ab02",
    "age-of-acquisition" = "#e7298a",
    "null" = "#4d4d4d"
  )) +
  scale_x_discrete(expand = expansion(add = c(0.1, 0.1))) +
    labs(x = NULL, y = "Rescaled BIC") +
    theme_minimal(base_size=9) +
    theme(
      panel.grid = element_blank(),
      legend.position = "none",
      axis.text.x = element_text(size = 10),
      axis.title.y = element_text(size = 10)
    )

}

fw <- make_fig(f_full_n, f_full_v, "lex_wold")  + ggtitle("WOLD (full set)")  +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
fi <- make_fig(f_full_n, f_full_v,  "lex_ids") + ggtitle("IDS (full set)")  +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
dw <- make_fig(f_dev_n, f_dev_v,  "lex_wold")  + ggtitle("WOLD (dev. set)")  +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))
di <- make_fig(f_dev_n, f_dev_v,  "lex_ids") + ggtitle("IDS (dev. set)")  +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

combo <- fi + fw + di + dw + 
  plot_layout(nrow=2, ncol = 2) + plot_annotation(tag_levels = 'A')

ggsave(here("output/figures", "noun_verb.pdf"), combo, width = 18, height = 20.25, units = "cm")

```

