---
title: "Pair analyses"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
```


```{r libraries}

library(tidyverse) 
library(here)
library(janitor)
library(patchwork)
library(ggrepel)
library(xtable)
library(DBI)
library(glmmTMB)

select <- dplyr::select
```

This notebook contains our analysis of concept pairs and analysis on the relationship between lexicalization and other phenomena.

## Analysis of concept pairs

We consider concept pairs from two different sources of data: the Small World of Words (SWOW) and the Database of Cross-Linguistic Colexifications (CLICS).

### Pairs from SWOW

Load word association data and find matching lemmas.

```{r load concepticon, include=TRUE}

set.seed(123)

d_full <- read_csv(here("data", "d_full.csv"), show_col_types = FALSE) 

d <- d_full %>%
  select(-ontological_category, -semantic_category, -wl_cvar, -do_cvar) %>%
  rename(aoa = aoa_self) %>%
  mutate(concepticon_gloss = str_to_lower(concepticon_gloss))

swow <- read_csv(here("rawdata/swow", "SWOW-EN.complete.20180827.csv"))

wp <- swow %>%
  group_by(cue, R1) %>%
  summarise(n = n_distinct(participantID)) %>%
  ungroup() %>%
  # given by at least two participants
  filter(n > 1) %>%
  rename(response = R1)

first <- wp %>%
  inner_join(d %>% rename(cue = concepticon_gloss), by = "cue") %>% unique()

all_wa <- first %>%
  inner_join(d %>%
               rename(response = concepticon_gloss, target_id = concepticon_id, target_field = semantic_field,
                      target_wold = lex_wold, target_ids = lex_ids, 
                      target_wl_mean = wl_mean, target_en = en, target_do_mean = do_mean,
                      target_ins = ins, target_aoa = aoa, target_conc = conc,
                      target_cd = cd, target_sens = sens),
               by = "response") %>%
  unique()

create_pairs <- function(data, lex, target_lex){

unique <- data %>%
  filter(cue != response) %>%
  mutate(pair_id = pmin(concepticon_id, target_id) %>% 
                    paste(pmax(concepticon_id, target_id), sep = "-")) %>%
  distinct(pair_id, .keep_all = TRUE) %>%
  select(-pair_id) %>%
  rename(lex_lang = {{lex}}, target_lex_lang = {{target_lex}})

cp1 <- unique %>%
  filter(lex_lang >= target_lex_lang)

cp2 <- unique %>%
  filter(lex_lang < target_lex_lang) %>%
  rename(cue= response, response = cue,
         concepticon_id = target_id, target_id = concepticon_id, 
         semantic_field = target_field, target_field = semantic_field,
         lex_lang = target_lex_lang, target_lex_lang = lex_lang,
         wl_mean = target_wl_mean, target_wl_mean = wl_mean,
         do_mean = target_do_mean, target_do_mean = do_mean,
         en = target_en, target_en = en,
         cd = target_cd, target_cd = cd,
         aoa = target_aoa, target_aoa = aoa,
         ins = target_ins, target_ins = ins,
         conc = target_conc, target_conc = conc,
         sens = target_sens, target_sens = sens
         )

cp <- bind_rows(cp1, cp2) %>%
  mutate(pair = paste0(cue, "-", response)) %>%
  mutate(normlex = lex_lang / (lex_lang + target_lex_lang),
         normmean_wl = wl_mean / (wl_mean + target_wl_mean),
         normmean_do = do_mean / (do_mean + target_do_mean),
         normen = en / (en + target_en),
         normcd = cd / (cd + target_cd),
         normaoa = aoa / (aoa + target_aoa),
         normins = ins / (ins + target_ins),
         normconc = conc / (conc + target_conc),
         normsens = sens / (sens + target_sens)) %>%
  select(pair:normsens) %>%
  unique()

bid <- cp %>%
  distinct(pair) %>%
  mutate(
    word1 = word(pair, 1, sep = fixed("-")),
    word2 = word(pair, 2, sep = fixed("-")),
    sorted_pair = ifelse(word1 < word2,
                         paste(word1, word2, sep = "-"),
                         paste(word2, word1, sep = "-"))
  ) %>%
  group_by(sorted_pair) %>%
  filter(n() > 1) %>%
  ungroup()
print(nrow(bid))

dup <- cp %>% 
  group_by(pair) %>% 
  mutate(n=n()) %>% 
  ungroup() %>% 
  filter(n > 1)
print(nrow(dup))

cp <- cp %>%
  # filter out bidirectional and duplicate cases
  filter(!(pair %in% c(bid$pair, dup$pair)))
print(nrow(cp))

return(cp)

}

analyse_pairs <- function(data){
  
  cp <- data

calculate_score <- function(pred1, pred2, reverse = FALSE) {
  if (pred1 == 0.5 || pred2 == 0.5) {
    return(0.5)
  } else if ((!reverse && ((pred1 > 0.5 & pred2 > 0.5) | (pred1 < 0.5 & pred2 < 0.5))) ||
             (reverse && ((pred1 > 0.5 & pred2 < 0.5) | (pred1 < 0.5 & pred2 > 0.5)))) {
    return(1) 
  } else {
    return(0) 
  }
}

correct_mean_wl <- mean(mapply(calculate_score, cp$normlex, cp$normmean_wl))
correct_mean_do <- mean(mapply(calculate_score, cp$normlex, cp$normmean_do))
correct_en <- mean(mapply(calculate_score, cp$normlex, cp$normen))
correct_cd <- mean(mapply(calculate_score, cp$normlex, cp$normcd))
correct_aoa <- mean(mapply(calculate_score, cp$normlex, cp$normaoa, reverse = TRUE))
correct_ins <- mean(mapply(calculate_score, cp$normlex, cp$normins))
correct_conc <- mean(mapply(calculate_score, cp$normlex, cp$normconc))
correct_sens <- mean(mapply(calculate_score, cp$normlex, cp$normsens))

results <- data.frame(
  variable = c("mean usage (Worldlex)", "mean usage (DoReCo)", 
               "usage (English only)", "contextual diversity",
               "AoA (self reported)", "association in-strength", 
               "concreteness", "sensorimotor"),
  correct.prediction = c(correct_mean_wl, correct_mean_do,
                         correct_en, correct_cd, 
                         correct_aoa, correct_ins, 
                         correct_conc, 
                         correct_sens)
) %>% arrange(desc(correct.prediction))

# Bootstrapping

set.seed(123)

n_boot <- 1000
n_rows <- nrow(cp)

calculate_correct_predictions <- function(data) {
  correct_score <- function(pred1, pred2, reverse = FALSE) {
    if (pred1 == 0.5 || pred2 == 0.5) {
      return(0.5) 
    } else if ((!reverse && ((pred1 > 0.5 & pred2 > 0.5) | (pred1 < 0.5 & pred2 < 0.5))) ||
               (reverse && ((pred1 > 0.5 & pred2 < 0.5) | (pred1 < 0.5 & pred2 > 0.5)))) {
      return(1)
    } else {
      return(0)
    }
  }
  
  correct_mean_wl <- mean(mapply(correct_score, data$normlex, data$normmean_wl))
  correct_mean_do <- mean(mapply(correct_score, data$normlex, data$normmean_do))
  correct_en <- mean(mapply(correct_score, data$normlex, data$normen))
  correct_cd <- mean(mapply(correct_score, data$normlex, data$normcd))
  correct_ins <- mean(mapply(correct_score, data$normlex, data$normins))
  correct_conc <- mean(mapply(correct_score, data$normlex, data$normconc))
  correct_aoa <- mean(mapply(correct_score, data$normlex, data$normaoa, reverse = TRUE))
  correct_sens <- mean(mapply(correct_score, data$normlex, data$normsens))
  
  c(correct_mean_wl, correct_mean_do, correct_en, 
    correct_cd, correct_aoa, correct_ins, correct_conc, correct_sens)
}


bootstrap_results <- replicate(n_boot, {
  sample_data <- cp[sample(1:n_rows, n_rows, replace = TRUE), ]
  calculate_correct_predictions(sample_data)
})

bootstrap_results <- t(bootstrap_results)
colnames(bootstrap_results) <- c("mean usage (Worldlex)","mean usage (DoReCo)",
                                  "usage (English only)", "contextual diversity",
                                  "AoA (self reported)", "association in-strength", 
                                  "concreteness", "sensorimotor")

ci <- apply(bootstrap_results, 2, function(x) quantile(x, probs = c(0.025, 0.975)))

results_with_ci <- data.frame(
  variable = colnames(bootstrap_results),
  lower.ci = ci[1, ],
  upper.ci = ci[2, ]
)


results_final <- results %>%
  left_join(results_with_ci, by = "variable") %>%
  mutate(variable = fct_reorder(variable, correct.prediction))

return(results_final)

}

wa_wold <- create_pairs(all_wa, "lex_wold", "target_wold")
wa_ids <- create_pairs(all_wa, "lex_ids", "target_ids")

wa_wold_result <- analyse_pairs(wa_wold) 
wa_ids_result <- analyse_pairs(wa_ids) 

# Bidirectional cases in SWOW have contained cases where e.g. male (of person) and male (of animal) or child (young human) and child (descendant) where normlex values were one above 0.5 and the other below 0.5.
# Duplicate cases include concepts e.g. ask (inquire) and ask (request) where normlex values were both above 0.5 or below 0.5.
# Because all predictor variables are based on the same lemma for e.g. male, we decided to take these out from our analysis.

```

### Pairs from CLICS

```{r semshift, include=FALSE}
clicsfile = here("rawdata", "clics.sqlite")

mydb <- dbConnect(RSQLite::SQLite(), clicsfile)

lt <- dbReadTable(mydb, 'LanguageTable')
pt <- dbReadTable(mydb, 'ParameterTable')

pid_gloss <- pt %>%
  select(ID, Concepticon_Gloss, Concepticon_ID) %>%
  rename(Parameter_ID=ID) %>%
  unique()

ft <- dbReadTable(mydb, 'FormTable') %>%
  left_join(pid_gloss, by = "Parameter_ID")

dbDisconnect(mydb)

ft1 <- ft %>%
  clean_names() %>% 
  select(language_id, concepticon_id, value) %>%
  # consider only those in our preprocessed data
  filter(concepticon_id %in% d_full$concepticon_id) %>%
  # filter out forms that are empty
  filter(!is.na(value) & value != "") %>%
  unique() %>%
  group_by(language_id, value) %>%
  summarise( n = n(),
    ids = str_c(concepticon_id, collapse = ", "), .groups = "drop") %>%
  ungroup() %>%
  filter(n != 1)

more2 <- ft1 %>%
  filter(n > 2) %>%  
  rowwise() %>%
  mutate(
    id_vec = list(str_split(ids, ",\\s*")[[1]]),               
    pairs = list(combn(id_vec, 2, simplify = FALSE))            
  ) %>%
  unnest(pairs) %>%
  mutate(
  pair = map_chr(pairs, ~ {
    .x_sorted <- .x[order(as.numeric(.x))]
    str_c(.x_sorted, collapse = "-")
  })
) %>%
  group_by(pair) %>%
  summarise(n = n_distinct(language_id)) %>%
  ungroup()

two <- ft1 %>%
  filter(n == 2) %>%
  rowwise() %>%
  mutate(
    pair = {
      id_vec <- str_split(ids, ",\\s*")[[1]]
      id_sorted <- id_vec[order(as.numeric(id_vec))]
      str_c(id_sorted, collapse = "-")
    }
  ) %>%
  group_by(pair) %>%
  summarise(n = n_distinct(language_id)) %>%
  ungroup()

uniq <- bind_rows(two, more2) %>% 
  unique() %>%
  # attested by at least 3 languages
  filter(n >= 3) %>%
  separate(pair, into = c("concepticon_id", "target_id"), sep = "-", convert = TRUE)

first <- uniq %>%
  inner_join(d %>% rename(cue = concepticon_gloss), by = "concepticon_id")

all_cl <- first %>%
  inner_join(d %>% rename(target_id = concepticon_id, response = concepticon_gloss, target_field = semantic_field,
                      target_wold = lex_wold, target_ids = lex_ids, 
                      target_wl_mean = wl_mean, target_en = en, target_do_mean = do_mean,
                      target_ins = ins, target_aoa = aoa, target_conc = conc,
                      target_cd = cd, target_sens = sens)
               , by = "target_id")

cl_wold <- create_pairs(all_cl, "lex_wold", "target_wold")
cl_ids <- create_pairs(all_cl, "lex_ids", "target_ids")

cl_wold_result <- analyse_pairs(cl_wold) 
cl_ids_result <- analyse_pairs(cl_ids) 

```

Combine all:

```{r all, include=TRUE}

all_all <- bind_rows(all_wa, all_cl) %>% unique()

all_wold <- create_pairs(all_all, "lex_wold", "target_wold")
all_ids <- create_pairs(all_all, "lex_ids", "target_ids")

all_wold_result <- analyse_pairs(all_wold) 
all_ids_result <- analyse_pairs(all_ids) 

```

Make a figure based on IDS and DoReCo:

```{r main fig, include=TRUE}
mytheme <- theme_minimal(base_size = 9) +
  theme(
    legend.position = "none",
    panel.grid.major = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    axis.line = element_line(color = "gray60", size = 0.3),
    axis.title = element_text(size = 12.375),
    axis.ticks.y = element_line(color = "black", size = 0.5),
    axis.text.x = element_text(size = 10.125),
    axis.text.y = element_text(size = 10.125),
    strip.text = element_text(size = 10.125, face = "bold")
  )

black_pairs <- c("water-reef", "fruit-fig","sea-tide", "soul-religion",
                 "wind-air","think-idea","rain-weather",  "grass-hay",
                 "fish-whale", "meal-dinner", "moon-tide", "food-farmer",
                 "bread-barley", "bird-eagle", "water-tide", "high-low", "inside-outside", "mouth-speech", "sun-clock",
                 "year-autumn", "many-thousand", "year-summer", "sick-healthy"
                 )

green_pairs <- c("circle-square", 
                 "red-yellow", "love-pity"
                 )

red_pairs <- c("love-hate")

pos_pairs <- c(black_pairs, green_pairs, red_pairs)

neg_black_pairs <-c ("day-hour","sweet-yam", "ocean-reef", "honey-bear", "age-time",
                     "milk-coconut", "deep-inside", "day-night", "wood-tree",
                     "sun-time", "green-plant", "moon-month")

neg_green_pairs <-c()

neg_red_pairs <- c("red-white")

neg_pairs <- c(neg_black_pairs, neg_green_pairs, neg_red_pairs)

plotd <- all_ids %>%
  mutate(highlight = ifelse(pair %in% c(pos_pairs, neg_pairs), "Highlighted", "Other")) %>%
  mutate(
    label_color = case_when(
      pair %in% green_pairs ~ "green",
      pair %in% red_pairs ~ "red",
      pair %in% neg_green_pairs ~ "green",
      pair %in% neg_red_pairs ~ "red",
      TRUE ~ "other"
    )
  )

set.seed(421)
sp <- ggplot(plotd, aes(x = normmean_do, y = normlex, text = pair)) +
  geom_vline(xintercept = 0.5, color = "gray60", linetype = "dashed", size = 0.3) +
  geom_point(data = filter(plotd, highlight == "Other"), 
             size = 0.1, color = "gray", alpha = 0.5, show.legend = FALSE) +
  geom_point(
  data = filter(plotd, highlight == "Highlighted"),
  aes(color = label_color),
  size = 0.8,
  alpha = 0.9,
  show.legend = FALSE
) +
  geom_label_repel(data = filter(plotd, pair %in% pos_pairs),
                   aes(label = pair, color = label_color),
                   size = 3.375, fill = "white", box.padding = 0.05,
                   point.padding = 0,
                   force = 0.2, force_pull = 4,
                   segment.color = "gray60", segment.size = 0.3,
                   min.segment.length = unit(1.5, "lines"),
                   label.size = NA) +
  geom_label_repel(data = filter(plotd, pair %in% neg_pairs),
                   aes(label = paste0("italic('", pair, "')"), color = label_color),
                   size = 3.375, fill = "white", box.padding = 0.05,
                   point.padding = 0,
                   force = 0.2, force_pull = 4,
                   segment.color = "gray60", segment.size = 0.3,
                   min.segment.length = unit(1.5, "lines"),
                   label.size = NA, parse = TRUE) +
  scale_color_manual(values = c(
  "green" = "#0072B2",  
  "red"   = "#D55E00",   
  "other" = "gray40"
)) +
  labs(
    x = "Normalized mean usage frequency",
    y = "Normalized lexicalization score",
    title = ""
  ) + 
  ylim(0.49, 0.754) +
  mytheme  + 
  theme(#axis.line = element_line(color = "gray70", size = 0.3),
        axis.ticks.y = element_blank()
        )

ggsave(here("output/figures", "ipa.pdf"), sp, width = 18, height = 15.75, units = "cm")
```

Make a figure for all datasets:

```{r main fig, include=TRUE}

set.seed(123)

wa_wold_result$lexsource <- "WOLD"
wa_ids_result$lexsource <- "IDS"
cl_wold_result$lexsource <- "WOLD"
cl_ids_result$lexsource <- "IDS"
all_wold_result$lexsource <- "WOLD"
all_ids_result$lexsource <- "IDS"

wa_wold_result$pairsource <- "SWOW (N=3257)"
wa_ids_result$pairsource <- "SWOW (N=3257)"
cl_wold_result$pairsource <- "CLICS (N=2074)"
cl_ids_result$pairsource <- "CLICS (N=2074)"
all_wold_result$pairsource <- "All pairs (N=4688)"
all_ids_result$pairsource <- "All pairs (N=4688)"

combined_data <- bind_rows(
  wa_wold_result,
  wa_ids_result,
  cl_wold_result,
  cl_ids_result,
  all_wold_result,
  all_ids_result
) %>%
  mutate(pairsource = factor(pairsource, levels=c("All pairs (N=4688)", "CLICS (N=2074)", "SWOW (N=3257)")))

d1 <- combined_data %>%
  filter(lexsource == "WOLD")

all_order <- d1 %>%
  filter(pairsource == "All pairs (N=4688)") %>%
  arrange(correct.prediction) %>%
  pull(variable)

p1 <- d1 %>%
  mutate(variable = factor(variable, levels = all_order)) %>%
  ggplot(aes(x = correct.prediction, y = variable, color = pairsource)) +
  geom_vline(xintercept = 0.5, size = 0.2, color = "gray60", linetype = "dashed") +
  geom_segment(aes(x = lower.ci, xend = upper.ci),
              position = position_dodge(width = 0.6), color = "gray", size = 0.3) +
  geom_point(size = 1.3) + 
  geom_text(aes(x = correct.prediction, label = round(correct.prediction, 2)),
            vjust = -1, size = 2.5, color = "gray60") +
  facet_wrap(~ pairsource, nrow=1) +
  scale_color_manual(
    values = c(
      "CLICS (N=2074)" = "#1b9e77",        
      "SWOW (N=3257)" = "#d95f02",       
      "All pairs (N=4688)" = "#7570b3"
    )
  ) +
  labs(x = "Proportion of correct predictions", y = "", color = "") +
  mytheme  +
  scale_x_continuous(breaks = c(0.5, 0.6, 0.7))
p1

d2 <- combined_data %>%
  filter(lexsource == "IDS")

all_order <- d2 %>%
  filter(pairsource == "All pairs (N=4688)") %>%
  arrange(correct.prediction) %>%
  pull(variable)

p2 <- d2 %>%
  mutate(variable = factor(variable, levels = all_order)) %>%
  ggplot(aes(x = correct.prediction, y = variable, color = pairsource)) +
  geom_vline(xintercept = 0.5, size = 0.2, color = "gray60", linetype = "dashed") +
  geom_segment(aes(x = lower.ci, xend = upper.ci),
              position = position_dodge(width = 0.6), color = "gray", size = 0.3) +
  geom_point(size = 1.3) +
  geom_text(aes(x = correct.prediction, label = round(correct.prediction, 2)),
            vjust = -1, size = 2.5, color = "gray60") +
  facet_wrap(~ pairsource, nrow=1) +
  scale_color_manual(
    values = c(
      "CLICS (N=2074)" = "#1b9e77",        
      "SWOW (N=3257)" = "#d95f02",       
      "All pairs (N=4688)" = "#7570b3"
    )
  ) +
  labs(x = "", y = "", color = "") +
  mytheme  +
  scale_x_continuous(breaks = c(0.5, 0.6, 0.7))
p2

final_plot <- p2 + p1 + 
  plot_layout(nrow=2, heights = c(1, 1)) +
  plot_annotation(tag_levels = 'A')

ggsave(here("output/figures", "pairs.pdf"), final_plot, width = 18, height = 18, units = "cm")

```


## Analysis on implicational universals

Implicational universals:

```{r semantic relation, include=TRUE}

high <- c("hand", "arm", 
          "white", "red", "yellow", "green", 
          "circle", 
          "east", "west",
          "hate", "anger", "guilty", "love", "fear", "anxiety", "proud", "surprised")

low <- c("foot", "leg", 
         "red", "yellow", "green", "blue", 
         "square",
         "north", "south",
         "love", "fear", "anxiety", "proud", "surprised", "pity")

d <- d_full %>%
  filter(concepticon_gloss %in% c(high, low)) %>%
  select(concepticon_gloss, lex_wold, lex_ids, wl_mean, do_mean) 


d1 <- d %>%
  filter(concepticon_gloss %in% high) %>%
  rename_with(~ paste0(.x, "1"))

d2 <- d %>%
  filter(concepticon_gloss %in% low) %>%
  rename_with(~ paste0(.x, "2"))

pairs <- c("hand-foot", "arm-leg", 
           "white-red", "red-yellow", "red-green", "red-blue", "yellow-blue", "green-blue",
           "circle-square", 
           "east-north", "west-north", "east-south", "west-south",
           "hate-love","hate-fear","hate-anxiety","hate-proud","hate-surprised","hate-pity",
           "anger-love","anger-fear","anger-anxiety","anger-proud","anger-surprised","anger-pity",
           "guilty-love","guilty-fear","guilty-anxiety","guilty-proud","guilty-surprised","guilty-pity",
           "love-anxiety","love-proud","love-surprised","love-pity",
           "fear-anxiety","fear-proud","fear-surprised","fear-pity",
           "anxiety-surprised","anxiety-pity","proud-surprised","proud-pity",
           "surprised-pity")

# For emotion pairs, we collected any terms from Fig 1 in Hupka et al. (1999) if they happen to exist in our data. If noun form does not exist but its adjective counterpart exist, we took the adjective (e.g. proud for pride, guilty for guilt). 

full <- d1 %>%
  cross_join(d2) %>%
  mutate(pair = paste0(concepticon_gloss1, "-", concepticon_gloss2)) %>%
  filter(pair %in% pairs) %>%
  mutate(wold = lex_wold1 / (lex_wold1 + lex_wold2) ,
         ids = lex_ids1 / (lex_ids1 + lex_ids2),
         wl = wl_mean1 / (wl_mean1 + wl_mean2),
         do = do_mean1 / (do_mean1 + do_mean2)) %>%
  select(pair, wold, ids, wl, do) %>%
  mutate(source = case_when(
    pair %in% c("hate-love","hate-fear","hate-anxiety","hate-proud","hate-surprised","hate-pity",
           "anger-love","anger-fear","anger-anxiety","anger-proud","anger-surprised","anger-pity",
           "guilty-love","guilty-fear","guilty-anxiety","guilty-proud","guilty-surprised","guilty-pity",
           "love-anxiety","love-proud","love-surprised","love-pity",
           "fear-anxiety","fear-proud","fear-surprised","fear-pity",
           "anxiety-surprised","anxiety-pity","proud-surprised","proud-pity",
           "surprised-pity") ~ "Hupka et al. 1999",
    pair %in% c("white-red", "red-yellow", "red-green", "red-blue", "yellow-blue", "green-blue") ~ "Berlin & Kay 1991",
    pair %in% c("hand-foot", "arm-leg") ~ "Andersen 1978",
    pair %in% c("circle-square") ~ "Burris 1978",
    pair %in% c("east-north", "west-north", "east-south", "west-south") ~ "Brown 1983"
  )) %>%
  rename(token = pair) %>%
  mutate(
    type = case_when(
    str_detect(token, "^hate-") ~ paste0("anger-", str_remove(token, "^hate-")),
    str_detect(token, "^anger-") ~ paste0("anger-", str_remove(token, "^anger-")),
    TRUE ~ token
    ))
```

First create a consensus set:

```{r}
consensus <- full %>%
  group_by(type) %>% 
  mutate(wold_mean = mean(wold), ids_mean = mean(ids)) %>%
  ungroup() %>%
  # need to be supported by at least one of the lexicalization datasets
  filter(wold_mean >= 0.5 & ids_mean >= 0.5) 
```

Run bootstrapping to estimate confidence intervals:

```{r}
run_bootstrap <- function(data, freq_col, n_boot = 1000, seed = 123) {
  
  set.seed(seed)
  
  compute_mean <- function(df) {
    df %>%
      group_by(type) %>%
      summarise(
        type_mean = mean(.data[[freq_col]], na.rm = TRUE),
        .groups = "drop"
      ) %>%
      summarise(
        mean_estimate = mean(type_mean, na.rm = TRUE)
      )
  }
  
  mean_val <- compute_mean(data)
  
  ci_vals <- map_dfr(1:n_boot, \(i) {
    data %>%
      slice_sample(n = nrow(data), replace = TRUE) %>%
      compute_mean() %>%
      mutate(sample = i)
  }) %>%
    summarise(
      lower = quantile(mean_estimate, 0.025),
      upper = quantile(mean_estimate, 0.975)
    )
  
  bind_cols(mean_val, ci_vals) %>%
    mutate(freq = freq_col)
}

confidence_intervals <- bind_rows(
  run_bootstrap(full, "wl") %>% mutate(dataset = "full"),
  run_bootstrap(full, "do") %>% mutate(dataset = "full"),
  run_bootstrap(consensus, "wl") %>% mutate(dataset = "consensus"),
  run_bootstrap(consensus, "do") %>% mutate(dataset = "consensus")
)
```

Estimate p-values based on the regression analyses:

```{r}
logit <- function(p) log(p / (1 - p))

run_glmm_test <- function(data, predictor) {
  
  dat <- data %>%
    select(type, token, all_of(predictor)) %>%
    mutate(
      # tranform to logit scale
      predictor_value = logit(.data[[predictor]]),
      # assume that the outcome variable has value of 1 when the direction of the universals is correct
      lud = 1
    )
  
  full_model <- glmmTMB(
    lud ~ 0 + predictor_value + (1 | type),
    data = dat,
    family = binomial(link = "logit")
  )
  
  null_model <- glmmTMB(
    lud ~ 0 + (1 | type),
    data = dat,
    family = binomial(link = "logit")
  )
  
  anova_result <- anova(null_model, full_model)
  
  tibble(
    predictor = predictor,
    p_value = anova_result$`Pr(>Chisq)`[2]
  )
}

p_values <- bind_rows(
  run_glmm_test(full, "wl") %>% mutate(dataset = "full"),
  run_glmm_test(full, "do") %>% mutate(dataset = "full"),
  run_glmm_test(consensus, "wl") %>% mutate(dataset = "consensus"),
  run_glmm_test(consensus, "do") %>% mutate(dataset = "consensus")
)
```

Make table:

```{r}
results_all <- confidence_intervals %>%
  left_join(p_values %>% rename(freq = predictor), by = c("dataset", "freq")) %>%
  select(dataset, freq, mean_estimate, lower, upper, p_value) %>%
  pivot_wider(
    names_from = freq,
    values_from = c(mean_estimate, lower, upper, p_value),
    names_glue = "{.value}_{freq}"
  ) %>%
  mutate(
    across(
      c(mean_estimate_do, lower_do, upper_do,
        mean_estimate_wl, lower_wl, upper_wl),
      ~ round(.x, 2)
    ),
    across(
      c(p_value_do, p_value_wl),
      ~ case_when(
        .x < 0.001 ~ as.character('< 0.001'),
        TRUE ~ sprintf("%.3f", .x)
      )
    ),
    ci_do = sprintf("[%.2f, %.2f]", lower_do, upper_do),
    ci_wl = sprintf("[%.2f, %.2f]", lower_wl, upper_wl)
  ) %>%
  select(
    dataset,
    mean_do = mean_estimate_do, ci_do, p_value_do,
    mean_wl = mean_estimate_wl, ci_wl, p_value_wl
  )

table_iu_freq <- xtable(
  results_all,
  digits = c(0, 0, 2, 0, 0, 2, 0, 0),
  label = "tab:iu_freq"
)

print(
  table_iu_freq,
  file = here("output", "tables", "iu_freq.tex"),
  include.rownames = FALSE,
  comment = FALSE,
  caption.placement = "top",
  hline.after = c(-1, 0, nrow(results_all))
)
```

Evaluate existing universals:

```{r}
wold <- read_csv(here("data", "wold_data.csv"), show_col_types = FALSE)
ids <- read_csv(here("data", "ids_data.csv"), show_col_types = FALSE) 

pairs <- full %>%
  select(type, token) %>%
  separate(token, into = c("concept1", "concept2"), sep = "-")

wold_pairs <- pairs %>%
  left_join(wold %>% distinct(glottocode, language, lex1 = lex, concept1 = concepticon_gloss), by = "concept1") %>%
  left_join(wold %>% distinct(glottocode, language, lex2 = lex, concept2 = concepticon_gloss), by = c("glottocode", "language", "concept2")) %>%
  # filter out languages that have NA values for the concepts
  filter(!is.na(lex1), !is.na(lex2)) %>%
  # filter out languages that have no lexicalization for both concepts
  filter(!(lex1 == 0 & lex2 == 0)) %>%
  # filter out languages that have lexicalization for both concepts
  filter(!(lex1 == 1 & lex2 == 1)) %>%
  mutate(support = case_when(
    lex1 == 1 & lex2 == 0 ~ 1,
    lex1 == 0 & lex2 == 1 ~ 0
  )) %>%
  group_by(type, glottocode, language) %>%
  summarise(support = mean(support)) %>%
  ungroup()

wold_pairs_sum <- wold_pairs %>%
  group_by(type) %>%
  summarise(n_langs = n(),
            prop_support = sum(support) / n_langs) %>%
  ungroup()

ids_pairs <- pairs %>%
  left_join(ids %>% distinct(glottocode, language=langname, lex1 = lex, concept1 = concepticon_gloss), by = "concept1") %>%
  left_join(ids %>% distinct(glottocode, language=langname, lex2 = lex, concept2 = concepticon_gloss), by = c("glottocode", "language", "concept2")) %>%
  # filter out languages that have NA values for the concepts
  filter(!is.na(lex1), !is.na(lex2)) %>%
  # filter out languages that have no lexicalization for both concepts
  filter(!(lex1 == 0 & lex2 == 0)) %>%
  # filter out languages that have lexicalization for both concepts
  filter(!(lex1 == 1 & lex2 == 1)) %>%
  mutate(support = case_when(
    lex1 == 1 & lex2 == 0 ~ 1,
    lex1 == 0 & lex2 == 1 ~ 0
  )) %>%
  group_by(type, glottocode, language) %>%
  summarise(support = mean(support)) %>%
  ungroup()

ids_pairs_sum <- ids_pairs %>%
  group_by(type) %>%
  summarise(n_langs = n(),
            prop_support = sum(support) / n_langs) %>%
  ungroup()

both_pairs_sum <- ids_pairs_sum %>%
  rename(ids_langs = n_langs, ids_prop = prop_support) %>%
  left_join(wold_pairs_sum %>% rename(wold_langs = n_langs, wold_prop = prop_support), by = "type")
```

Make table for a list of universals: 

```{r}
blue_ids <- both_pairs_sum %>%
  filter(ids_prop == 1) %>%
  pull(type)

red_ids <- both_pairs_sum %>%
  filter(ids_prop < 1) %>%
  pull(type)

blue_wold <- both_pairs_sum %>%
  filter(wold_prop == 1) %>%
  pull(type)

red_wold <- both_pairs_sum %>%
  filter(wold_prop < 1) %>%
  pull(type)

score_fun <- function(x) {
  case_when(
    x == "+" ~ 2,
    x == "0" ~ 1,
    TRUE ~ 0
  )
}

combo_cti <- full %>%
  group_by(type, source) %>%
  summarise(
    across(c(wold, ids, do, wl), ~ mean(.x, na.rm = TRUE)),
    .groups = "drop"
  ) %>%
  mutate(
    across(c(wold, ids, do, wl), ~ case_when(
      .x > 0.5 ~ "+",
      .x == 0.5 ~ "0",
      TRUE ~ "-"
    ))
  ) %>%
  mutate(
    lex_score = score_fun(wold) + score_fun(ids),
    freq_score = score_fun(do) + score_fun(wl),
    lex_match = as.integer(wold == ids),
    freq_match = as.integer(do == wl)
  ) %>%
  arrange(
    desc(lex_score), desc(lex_match),
    desc(freq_score), desc(freq_match)
  ) %>%
  select(-lex_score, -freq_score, -lex_match, -freq_match)

combo_cti_latex <- combo_cti_latex <- combo_cti %>%
  mutate(
    ids = if_else(type %in% blue_ids & ids == "+",
                  "\\textcolor{myblue}{+}", ids),
    wold = if_else(type %in% blue_wold & wold == "+",
                   "\\textcolor{myblue}{+}", wold)
  ) %>%
  mutate(
    ids = if_else(type %in% red_ids & ids == "+",
                  "\\textcolor{myred}{+}", ids),
    wold = if_else(type %in% red_wold & wold == "+",
                   "\\textcolor{myred}{+}", wold)
  ) %>%
  mutate(
    ids = if_else(type %in% red_ids & ids == "-",
                  "\\textcolor{myred}{-}", ids),
    wold = if_else(type %in% red_wold & wold == "-",
                   "\\textcolor{myred}{-}", wold)
  ) %>%
  separate(type, into = c("x", "y"), sep = "-", remove = FALSE) %>%
  mutate(type = str_glue("\\concept{{{x}}}~$\\iu$~\\concept{{{y}}}")) %>%
  select(type, source, ids, wold,do,wl)

table_cti <- xtable(
  combo_cti_latex,
  digits = c(0, rep(0, ncol(combo_cti_latex))),
  label = "tab:ipalong_cti"
)

print(
  table_cti,
  file = here("output", "tables", "ipa.tex"),
  include.rownames = FALSE,
  tabular.environment = "longtable",
  floating = FALSE,
  comment = FALSE,
  caption.placement = "top",
  hline.after = c(-1, 0, nrow(combo_cti_latex))
)
```

Make a table that contains raw relative scores:

```{r}
type_order <- combo_cti %>%
  distinct(type) %>%
  mutate(type_id = row_number())

df <- full %>%
  select(type, token, ids, wold, do, wl) %>%
  left_join(type_order, by = "type") %>%
  separate(type, into = c("type_x", "type_y"), sep = "-", remove = FALSE) %>%
  separate(token, into = c("token_x", "token_y"), sep = "-", remove = FALSE) %>%
  mutate(
    type = str_glue("\\concept{{{type_x}}}~$\\iu$~\\concept{{{type_y}}}"),
    token = str_glue("\\term{{{token_x}}}~$\\iu$~\\term{{{token_y}}}")
  ) %>%
  select(-type_x, -type_y, -token_x, -token_y) %>%
  arrange(type_id, token) %>%
  select(-type_id)

table_raw <- xtable(
  df,
  digits = c(0, 0, 0, 4, 4, 4, 4),
  label = "tab:iu_raw"
)

print(
  table_raw,
  file = here("output", "tables", "iu_raw.tex"),
  include.rownames = FALSE,
  comment = FALSE,
  caption.placement = "top",
  hline.after = c(-1, 0, nrow(df))
)
```

Identify new implicational universals:

```{r imp.uni include=TRUE}
# WOLD
wold_total <- length(unique(wold$glottocode))

wold <- wold %>%
  mutate(concepticon_id = as.character(concepticon_id)) %>%
  group_by(concepticon_id) %>%
  mutate(total = sum(lex),
         n = n()) %>%
  ungroup() %>%
  # filter out absolute universals
  filter(total != wold_total)

combos <- wold %>%
  select(semantic_field, concepticon_id) %>%
  unique() %>%
  group_by(semantic_field) %>%
  summarise(pairs = list(combn(concepticon_id, 2, simplify = FALSE)), .groups = "drop") %>%
  unnest(pairs) %>%
  mutate(concepticon_id1 = map_chr(pairs, 1),
         concepticon_id2 = map_chr(pairs, 2)) %>%
  select(-pairs)

wold1 <- wold %>%
  select(-total, -n) %>%
  rename_with(~ paste0(.x, "1"), -c(semantic_field, glottocode, language))

wold2 <- wold %>%
  select(-total, -n) %>%
  rename_with(~ paste0(.x, "2"), -c(semantic_field, glottocode, language))

result <- combos %>%
  left_join(wold1, by = c("semantic_field", "concepticon_id1")) %>%
  left_join(wold2, by = c("semantic_field", "concepticon_id2", "glottocode", "language")) %>%
  unique()

imp <- result %>%
  # these cases do not tell us about anything, so filter them out
  filter(!(lex1 == 1 & lex2 == 1) & !(lex1 == 0 & lex2 == 0)) %>%
  mutate(lex_diff = lex1 - lex2) %>%
  group_by(semantic_field, concepticon_id1, concepticon_gloss1, concepticon_id2, concepticon_gloss2) %>%
  summarise(
    langs = n_distinct(glottocode),
    lex1lex0 = sum(lex_diff == 1),
    lex0lex1 = sum(lex_diff == -1)
  ) %>%
  ungroup() %>%
  filter(!(lex1lex0 != 0 & lex0lex1 != 0))

a <- imp %>%
  filter(lex1lex0 != 0) %>%
  select(-lex1lex0, -lex0lex1) %>%
  rename(evidence = langs)

b <- imp %>%
  filter(lex1lex0 == 0) %>%
  select(-lex1lex0, -lex0lex1) %>%
  rename(concepticon_id1 = concepticon_id2,
         concepticon_gloss1 = concepticon_gloss2,
         concepticon_id2 = concepticon_id1,
         concepticon_gloss2 = concepticon_gloss1,
         evidence = langs)

all <- bind_rows(a, b) %>%
  #filter(evidence >= 20) %>%
  arrange(semantic_field) %>%
  write_csv(here("output/results", "imp_wold.csv"))

# IDS
ids_total <- length(unique(ids$language_id))

ids <- ids %>%
  mutate(concepticon_id = as.character(concepticon_id)) %>%
  group_by(concepticon_id) %>%
  mutate(total = sum(lex),
         n = n()) %>%
  ungroup() %>%
  # filter out absolute universals
  filter(total != ids_total)

combos <- ids %>%
  select(semantic_field, concepticon_id) %>%
  unique() %>%
  group_by(semantic_field) %>%
  filter(n() > 1) %>%  
  summarise(pairs = list(combn(concepticon_id, 2, simplify = FALSE)), .groups = "drop") %>%
  unnest(pairs) %>%
  mutate(concepticon_id1 = map_chr(pairs, 1),
         concepticon_id2 = map_chr(pairs, 2)) %>%
  select(-pairs)

ids1 <- ids %>%
  select(-total, -n) %>%
  rename_with(~ paste0(.x, "1"), -c(semantic_field, language_id, glottocode, langname))

ids2 <- ids %>%
  select(-total, -n) %>%
  rename_with(~ paste0(.x, "2"), -c(semantic_field, language_id, glottocode, langname))

result <- combos %>%
  left_join(ids1, by = c("semantic_field", "concepticon_id1")) %>%
  left_join(ids2, by = c("semantic_field", "concepticon_id2", "language_id", "glottocode", "langname")) %>%
  unique()

imp <- result %>%
  # these cases do not tell us about anything, so filter them out
  filter(!(lex1 == 1 & lex2 == 1) & !(lex1 == 0 & lex2 == 0)) %>%
  mutate(lex_diff = lex1 - lex2) %>%
  group_by(semantic_field, concepticon_id1, concepticon_gloss1, concepticon_id2, concepticon_gloss2) %>%
  summarise(
    langs = n_distinct(language_id),
    lex1lex0 = sum(lex_diff == 1),
    lex0lex1 = sum(lex_diff == -1)
  ) %>%
  ungroup() %>%
  filter(!(lex1lex0 != 0 & lex0lex1 != 0))

a <- imp %>%
  filter(lex1lex0 != 0) %>%
  select(-lex1lex0, -lex0lex1) %>%
  rename(evidence = langs)

b <- imp %>%
  filter(lex1lex0 == 0) %>%
  select(-lex1lex0, -lex0lex1) %>%
  rename(concepticon_id1 = concepticon_id2,
         concepticon_gloss1 = concepticon_gloss2,
         concepticon_id2 = concepticon_id1,
         concepticon_gloss2 = concepticon_gloss1,
         evidence = langs)

all <- bind_rows(a, b) %>%
  arrange(semantic_field) %>%
  write_csv(here("output/results", "imp_ids.csv"))
```
